A Technique for Inter-Catalogue Recommendations

### 2014-06-11 paper2/paper.tex
Change references to "latent space" to "concept space" to be more consistent.

Using random walks to simulate user data, followed by the application of LSI, is
indeed an effective way to encode information from a recommendation graph into a
latent feature space. But what is the relationship between latent feature
vectors derived from disconnected graph partitions? In principle, there is no
guarantee of any relationship between such latent spaces in the same way that
there is no guarantee of any relationship between two arbitrary, disconnected
recommendation graphs. Nonetheless, our hypothesis is that a relationship
between such latent spaces often will exist due to the effectiveness of the
underlying CF techniques that generate the graphs to capture meaningful
item-item associations. Put another way, we believe that the most fundamental
latent dimensions along which products in a category such as Women's swimsuits
vary will be common to many swimsuit catalogues. If this is indeed true, then it
might be possible to learn a mapping between these latent spaces.

If a mapping between the latent spaces associated with two catalogues were
known, we could translate all items into a common space and then choose
inter-catalogue edges between item pairs that are nearest to one another in
concept space. To learn these mapping, we must revisit the notion of content
similarity. Once again, we utilize tf-idf vectors. This time, however, we weight
an item $i$'s tf-idf vector $\vec{\tau}(i)$ by the elements in its latent
feature vector $\vec{v}(i)$. In this way, we construct a dense {\em
super-tf-idf} vector for each concept for each catalogue. Formally, we say that
a concept $j$ of a catalogue $C$ is represented by the super-tf-idf vector
\begin{align}
\vec{s}(j,C) = \sum_{i \in C}{v(i)_j \cdot \vec{\tau}(i)},
\end{align}
where $v(i)_j$ is the $j$\textsuperscript{th} component of item $i$'s latent
feature vector. These super-tf-idf vectors act as a proxy for the concept. We
approximate the mapping between two concept spaces by taking inner products of
super-tf-idf vectors. The details of this mapping process are provided in a
subsequent section.

>>>>

Using random walks to simulate user data, followed by the application of LSI, is
indeed an effective way to encode information from a recommendation graph into a
latent feature space. But what is the relationship between latent feature
vectors derived from disconnected graph partitions? In principle, there is no
guarantee of any relationship between such concept spaces in the same way that
there is no guarantee of any relationship between two arbitrary, disconnected
recommendation graphs. Nonetheless, our hypothesis is that a relationship
between these concept spaces often will exist due to the effectiveness of the
underlying CF techniques that generate the graphs to capture meaningful
item-item associations. Put another way, we believe that the most fundamental
latent dimensions along which products in a category such as Women's swimsuits
vary will be common to many swimsuit catalogues. If this is indeed true, then it
might be possible to learn a mapping between these concept spaces.

If a mapping between the concept spaces associated with two catalogues were
known, we could translate all items into a common space and then choose
inter-catalogue edges between item pairs that are nearest to one another in
concept space. To learn these mapping, we must revisit the notion of content
similarity. Once again, we utilize tf-idf vectors. This time, however, we weight
an item $i$'s tf-idf vector $\vec{\tau}(i)$ by the elements in its latent
feature vector $\vec{v}(i)$. In this way, we construct a dense {\em
super-tf-idf} vector for each concept for each catalogue. Formally, we say that
a concept $j$ of a catalogue $C$ is represented by the super-tf-idf vector
\begin{align}
\vec{s}(j,C) = \sum_{i \in C}{v(i)_j \cdot \vec{\tau}(i)},
\end{align}
where $v(i)_j$ is the $j$\textsuperscript{th} component of item $i$'s latent
feature vector. These super-tf-idf vectors act as a proxy for the concept. We
approximate the mapping between two concept spaces by taking inner products of
super-tf-idf vectors. The details of this mapping process are provided in a
subsequent section.
